---
output:
  html_document:
    theme: cerulean
  pdf_document: default
---

RIVUR - DEFA1A3 (SUBSET = ASIAN) 
===========
```{r output, eval = F, echo = F}
output:
  knitrBootstrap::bootstrap_document:
    theme: default
    highlight: sunburst
    theme.chooser: TRUE
    highlight.chooser: TRUE
```

```{r setting, message = FALSE, echo=FALSE}
# output:
#   knitrBootstrap::bootstrap_document:
#     theme.chooser: T
#     highlight.chooser: FALSE
#     menu: F
#     title: "IGLL5 report"
library(xlsx)
library(car)
library(knitr)
library(xtable)
library(dplyr)
library(ggplot2)
library(reshape2)
library(magrittr)
library(gridExtra)
library(gmodels)
library(psych)
library(tabplot)
opts_chunk$set(dev=c("svg"), 
              fig.height = 6, fig.width = 8)
opts_chunk$set(fig.show="hold")
opts_chunk$set(warning=F, message = FALSE, echo=F, results='asis')
opts_chunk$set(bootstrap.thumbnail.size='col-md-12', 
               bootstrap.thumbnail = T,
               bootstrap.panel = T)

# source("/Users/DL/Documents/R project/Memphis - Copy Number Variation/Functions/myFunction.R")
 
```

```{r myfunction, echo = F}
science_theme = theme(panel.grid.major = element_line(size = 0.4, color = "grey"),
                      axis.line = element_line(size = 0.5, color = "black"), 
                      legend.position = "none", 
#                       legend.position = c(0.85, 0.85),
                      plot.title = element_text(lineheight=.8, size = 10,  face="bold"),
                      text = element_text(size = 14))  
plt_s <- function(df, x, y){
        ggplot(df, aes_string(y = y, x = x)) +
        geom_boxplot() +
        scale_y_continuous(breaks = 3:14) +
        theme_bw() +
        science_theme
}

plt_oneway <- function(df, x, y){
        p = oneway.test(as.formula(paste0(y," ~ ",x)), data = df)$p.value
#         print(p)
        if(p > 0.2 | p == "NaN" | !exists("p")) {
                ggplot(df, aes_string(y = y, x = x)) +
                geom_boxplot() +
                scale_y_continuous(breaks = 3:14) +
                theme_bw() +
                science_theme
        } else
                ggplot(df, aes_string(y = y, x = x)) +
                geom_boxplot(aes_string(fill = x)) +
                scale_y_continuous(breaks = 3:14) +
                theme_bw() +
                science_theme
}

plt <- function(df, x, y){
        df_l = "rva1a3_array[!is.na(rva1a3_array[x]) & (rva1a3_array[x] != 'NA'), ]"
        para <- paste0("(",df_l,"$",y,", ", df_l,"$",x, ")")
        FUN_TABLE <- paste0("table",  para)
        p.chisq = chisq.test(eval(parse(text = FUN_TABLE)))$p.value
        p = p.chisq
        print(p)
        if(p > 0.2 | p == "NaN" | !exists("p")) {
                ggplot(df, aes_string(y = y, x = x)) +
                        geom_boxplot() +
                        scale_y_continuous(breaks = 3:14) +
                        theme_bw() +
                        science_theme
        } else
                ggplot(df, aes_string(y = y, x = x)) +
                geom_boxplot(aes_string(fill = x)) +
                scale_y_continuous(breaks = 3:14) +
                theme_bw() +
                science_theme
}

plt_point_s <- function(df, x, y){
        ggplot(df, aes_string(y = y, x = x)) +
        geom_point(position = "") +
        stat_sum(aes(size = ..n..)) +
        scale_y_continuous(breaks = 3:14) +
        scale_x_discrete() +
        theme_bw() +
        science_theme
}

plt_point <- function(df, x, y){
#         oneway_p = oneway.test(as.formula(paste0(y," ~ ",x)), data = df)$p.value
        df_l = "rva1a3_array[!is.na(rva1a3_array[x]) & (rva1a3_array[x] != 'NA'), ]"
        para <- paste0("(",df_l,"$",y,", ", df_l,"$",x, ")")
        FUN_TABLE <- paste0("table",  para)
        p.chisq = chisq.test(eval(parse(text = FUN_TABLE)))$p.value
        p = p.chisq
#         print(p)
        if(p > 0.2| p == "NaN") {
                ggplot(df, aes_string(y = y, x = x)) +
                        geom_point(position = "") +
                        stat_sum(aes(size = ..n..)) +
                        scale_y_continuous(breaks = 3:14) +
                        scale_x_discrete() +
                        theme_bw() +
                        science_theme
        }else
                ggplot(df, aes_string(y = y, x = x)) +
                geom_point(position = "", col = "blue") +
                stat_sum(aes(size = ..n..), col = "blue") +
                scale_y_continuous(breaks = 3:14) +
                scale_x_discrete() +
                theme_bw() +
                science_theme
}

```

```{r data_load_preprocessing, cache=T, message = FALSE, echo=F, results='asis'}

rva1a3_array <- read.xlsx("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/RIVUR data/RIVUR Spreadsheets/RV111201 A1A3 and Array Master Factors.xls", sheetIndex = 1, header = T, stringsAsFactors = T) %>% tbl_df
names(rva1a3_array) = toupper(names(rva1a3_array))
rva1a3_array$TXGROUP_LABEL = recode(rva1a3_array$TXGROUP, 
                             "'A' = 'TMP/SMZ'; 
                              'P' = 'Placebo'
                             ")
rva1a3_array$TF02_LABEL = recode(rva1a3_array$TF02, 
                             "1 = 'Treatment Failure'; 
                              0 = 'No Treatment Failure'
                             ")
rva1a3_array$RACE0102_LABEL = recode(rva1a3_array$RACE0102, 
                             "1 = 'White'; 
                              2 = 'Black';
                              3 = 'Asian';
                              4 = 'Hawaiian/Pacific Islander ';
                              5 = 'American Indian/Alaskan';
                              6 = 'Other';
                              7 = 'Mixed';
                              8 = 'Missing'
                             ")

# rva1a3_array = filter(rva1a3_array, RACE0102_LABEL == 'Asian')

# str(rva1a3)
# dim(rva1a3)
# names(rva1a3)
# names(rva1a3_array)
# IQR(rva1a3_array$DEFA1.A3.CN, na.rm = T)
# prop.table(table(rva1a3_array$DEFA1.A3.CN))
# quantile(rva1a3_array$DEFA1.A3.CN, na.rm = T, probs = 0.01)
# boxplot(rva1a3_array$DEFA1.A3.CN, notch = T, varwidth = T)
# 
# CrossTable(x = rva1a3_array$AGE0101, y = rva1a3_array$RACE0102)

# pairs.panels(rva1a3_array[c("AGE0101","RACE0102","SEX0101", "DEFA1.A3.CN")])

```

## Data summary
```{r summary - table, eval = F}
# rva1a3_array %>% group_by(ETHNIC0101, SEX0101) %>%
#         summarize(mean(DEFA1.A3.CN), n()) -> t1
# 
rva1a3_array %>% group_by(RACE0102) %>%
        summarize(DEFA1A3.mean = mean(DEFA1.A3.CN), Nbs = n()) -> t2
# 
# rva1a3_array %>% group_by(RaceEth, SEX0101) %>%
#         summarize(mean(DEFA1.A3.CN), n()) -> t3

# kable(t1)
# kable(t2)
# kable(t3)

```

```{r summary - plot, fig.height = 7, fig.width = 10}
par(mfrow = c(2,3))
hist(rva1a3_array$AGE0101, xlab = "Age",breaks = 20, main = "")
plot(as.factor(rva1a3_array$RACE0102_LABEL), breaks = 7, xlab = "Race", main = "")
plot(factor(rva1a3_array$SEX0101), xlab = "Sex", main = "")
hist(rva1a3_array$DEFA1.A3.CN, xlab = "DEFA1A3.CN", breaks = 12, main = "")
plot(rva1a3_array$TXGROUP_LABEL, xlab = "Treatment group assignment")
plot(as.factor(rva1a3_array$TF02_LABEL), xlab = "Treatment failure")
```

## Correlation
### Race & Gender 
```{r cor - Race & Gender, fig.height = 4, fig.width = 14}
rva1a3_array$RACE0102_LABEL = recode(rva1a3_array$RACE0102, 
                             "1 = 'White'; 
                              2 = 'Black';
                              3 = 'Asian';
                              4 = 'Hawaiian/Pacific Islander ';
                              5 = 'American Indian/Alaskan';
                              6 = 'Other';
                              7 = 'Mixed';
                              8 = 'Missing'
                             ")

va <- c("RACE0102_LABEL", "SEX0101")

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))

# par(mfrow = c(1,2))
# boxplot(DEFA1.A3.CN ~ RACE0102_LABEL, data = rva1a3_array, 
#         xlab = "Race", ylab = "DEFA1.A3.CN",
#         col = rainbow(7),
#         notch = T)
# boxplot(DEFA1.A3.CN ~ SEX0101, data = rva1a3_array, 
#         xlab = "Sex", ylab = "DEFA1.A3.CN",
#         notch = T, varwidth = F)

```

### Bladder and bowel movement dysfunction
```{r cor - BBD, fig.height = 4, fig.width = 14}
rva1a3_array$dtBBD = rva1a3_array$BBD1302 - rva1a3_array$BBD0102
rva1a3_array$dtBBD_LABEL = recode(rva1a3_array$dtBBD, 
                             "1 = 'Worse'; 
                              0 = 'No Change';
                             -1 = 'Better'")

va <- c("BBD0102", "BBD1302", "dtBBD_LABEL")

rva1a3_array$BBD0102 = as.factor(rva1a3_array$BBD0102)
rva1a3_array$BBD1302 = as.factor(rva1a3_array$BBD1302)
rva1a3_array$dtBBD_LABEL = as.factor(rva1a3_array$dtBBD_LABEL)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))
# 
# par(mfrow = c(1,3))
# boxplot(DEFA1.A3.CN ~ BBD0102, data = rva1a3_array, 
#         xlab = "BBD0102", ylab = "DEFA1.A3.CN")
# boxplot(DEFA1.A3.CN ~ BBD1302, data = rva1a3_array, 
#         xlab = "BBD1302", ylab = "DEFA1.A3.CN")
# boxplot(DEFA1.A3.CN ~ dtBBD_EXP, data = rva1a3_array, 
#         xlab = "dtBBD_EXP", ylab = "DEFA1.A3.CN",
#         col = rainbow(3), notch = T)
```


```{r ddBBD by TXGROUP, eval = F}
ggplot(rva1a3_array, aes(x = dtBBD_EXP, y = DEFA1.A3.CN, fill = dtBBD_EXP)) +
        geom_boxplot() +
        geom_point(position = "jitter")+
        scale_y_discrete(limits = c(3:14)) +
        facet_grid(.~TXGROUP) +
        theme_bw() +
        science_theme +
        scale_fill_brewer(palette = "Set3")
# 
# rva1a3_array %>% 
#         group_by(dtBBD_EXP) %>%
#         summarise(mean(DEFA1.A3.CN, na.rm = T), n())

```


```{r cor-TF02, fig.height = 4, fig.width = 12, eval = F}
### TF02
rva1a3_array$TF02_LABLE = recode(rva1a3_array$TF02, 
                             "1 = 'Treatment Failure'; 
                              0 = 'No Treatment Failure'
                             ")

# par(mfrow = c(1,1))
# boxplot(DEFA1.A3.CN ~ TF02_LABLE, data = rva1a3_array, 
#         xlab = "TF02", ylab = "DEFA1.A3.CN")

ggplot(rva1a3_array, aes(x = TF02_LABLE, y = DEFA1.A3.CN, fill =TF02_LABLE)) +
        geom_boxplot() +
        geom_point(position = "jitter")+
        scale_x_discrete() +
        facet_grid(.~TXGROUP) +
        theme_bw() +
        science_theme 


```

```{r cor-TF02 table, eval = F}
rva1a3_array %>% 
        group_by(TF02_LABLE, TXGROUP) %>%
        summarise(DEFA1A3.median = median(DEFA1.A3.CN, na.rm = T), Nbs = n()) %>% 
        kable(align = "l")
```

### DVQ SCORE
```{r cor-DVQSCORE, fig.height = 4, fig.width = 12}
rva1a3_array$DVQSCORE1304_CUT = cut(as.numeric(rva1a3_array$DVQSCORE1304), breaks = 2)
rva1a3_array$DVQSCORE0104_CUT = cut(as.numeric(rva1a3_array$DVQSCORE0104), breaks = 3)
rva1a3_array$dtDVQSCORE = unclass(rva1a3_array$DVQSCORE1304) - unclass(rva1a3_array$DVQSCORE0104)

# va <- c("CHR_CONST0102", "CHR_CONST1302", "dtCHR_CONST_LABEL")
va <- c("DVQSCORE0104_F", "DVQSCORE1304_F", "dtDVQSCORE" )
# , "dtDVQSCORE"
rva1a3_array$DVQSCORE0104_F = as.factor(rva1a3_array$DVQSCORE0104)
rva1a3_array$DVQSCORE1304_F = as.factor(rva1a3_array$DVQSCORE1304)
rva1a3_array$dtDVQSCORE = as.factor(rva1a3_array$dtDVQSCORE)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

# par(mfrow = c(1,3))
# plot(DVQSCORE0104 ~ DEFA1.A3.CN, data = rva1a3_array, 
#         ylab = "DVQSCORE0104", xlab = "DEFA1.A3.CN")
# plot(DVQSCORE1304 ~ DEFA1.A3.CN, data = rva1a3_array, 
#         ylab = "DVQSCORE1304", xlab = "DEFA1.A3.CN")
# plot(dtDVQSCORE ~ DEFA1.A3.CN, data = rva1a3_array, 
#         ylab = "dtDVQSCORE", xlab = "DEFA1.A3.CN")

# lm(DVQSCORE1304 ~ DEFA1.A3.CN, data = rva1a3_array)%>%summary

# ggplot(rva1a3_array[!is.na(rva1a3_array$DEFA1.A3.CN), ], aes(x = factor(DEFA1.A3.CN), y = DVQSCORE0104)) + 
# #         geom_boxplot() +
#         geom_point(position = "")+
#         geom_smooth(method = "lm") +
#         stat_sum(aes(size = ..n..)) +
# 
# #         xlim = c(3, 14) +
# #         scale_x_discrete() +
# #         facet_grid(.~TXGROUP) +
#         theme_bw() +
#         science_theme -> p1
# 
# ggplot(rva1a3_array[!is.na(rva1a3_array$DEFA1.A3.CN), ], aes(y = DEFA1.A3.CN, x = DVQSCORE1304)) +
# #         geom_boxplot() +
#                 geom_point(position = "", col = "blue") +
#                 stat_sum(aes(size = ..n..), col = "blue") +
#                 scale_y_continuous(breaks = 3:14) +
#                 scale_x_discrete() +
# 
# #         xlim = c(3, 14) +
# #         scale_x_discrete() +
# #         facet_grid(.~TXGROUP) +
#                 theme_bw() +
#                 science_theme -> p2
# 
# ggplot(rva1a3_array[!is.na(rva1a3_array$DEFA1.A3.CN), ], aes(x = factor(DEFA1.A3.CN), y = dtDVQSCORE)) +
# #         geom_boxplot() +
#         geom_point(position = "", fill = "black", col = "blue")+
#         geom_smooth(method = "lm") +
#         stat_sum(aes(size = ..n..), col = "blue") +
# 
# #         xlim = c(3, 14) +
# #         scale_y_discrete() +
# #         facet_grid(.~TXGROUP) +
#         theme_bw() +
#         science_theme -> p3
# 
# plot = list()
# plot = list(p1, p2, p3)
# do.call(grid.arrange, c(plot, list(nrow = 1, ncol =3)))

```

### Chronic constipation
```{r cor-CHR_CONST, fig.height = 4, fig.width = 14}
rva1a3_array$dtCHR_CONST = unclass(rva1a3_array$CHR_CONST1302) - unclass(rva1a3_array$CHR_CONST0102)

rva1a3_array$dtCHR_CONST_LABEL = recode(rva1a3_array$dtCHR_CONST, 
                             "-1 = 'Better'; 
                               0 = 'No Change';
                               1 = 'Worse'
                             ")

# par(mfrow = c(1,3))
# boxplot(DEFA1.A3.CN ~ CHR_CONST0102, data = rva1a3_array, 
#         xlab = "CHR_CONST0102", ylab = "DEFA1.A3.CN", 
#         notch = T, col = rainbow(2))
# boxplot(DEFA1.A3.CN ~ CHR_CONST1302, data = rva1a3_array, 
#         xlab = "CHR_CONST1302", ylab = "DEFA1.A3.CN",
#         notch = T)
# boxplot(DEFA1.A3.CN ~ dtCHR_CONST_LABEL, data = rva1a3_array, 
#         xlab = "dtCHR_CONST_LABEL", ylab = "DEFA1.A3.CN",
#         col = rainbow(3), notch = T)

va <- c("CHR_CONST0102", "CHR_CONST1302", "dtCHR_CONST_LABEL")

rva1a3_array$CHR_CONST0102 = as.factor(rva1a3_array$CHR_CONST0102)
rva1a3_array$CHR_CONST1302 = as.factor(rva1a3_array$CHR_CONST1302)
rva1a3_array$dtCHR_CONST = as.factor(rva1a3_array$dtCHR_CONST)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

```

### DMSA scan results
#### Scarring for right side
```{r cor-DMSA-right, fig.height = 4, fig.width = 14}
rva1a3_array$dtDM6A = (unclass(rva1a3_array$DM6A_13) - unclass(rva1a3_array$DM6A_01)) %>% as.factor

rva1a3_array$DM6A_01_LABEL = recode(rva1a3_array$DM6A_01, 
                             "'A' = 'None'; 
                              'B' = 'Mild';
                              'C' = 'Moderate';
                              'D' = 'Severe';
                              'E' = 'G. Atrophy'
                             ")
rva1a3_array$DM6A_01_LABEL = factor(rva1a3_array$DM6A_01_LABEL, c("None", 'Mild', 'Moderate', 'Severe', 'G. Atrophy'))

rva1a3_array$DM6A_13_LABEL = recode(rva1a3_array$DM6A_13, 
                             "'A' = 'None'; 
                              'B' = 'Mild';
                              'C' = 'Moderate';
                              'D' = 'Severe';
                              'E' = 'G. Atrophy'
                             ")
rva1a3_array$DM6A_13_LABEL = factor(rva1a3_array$DM6A_13_LABEL, c("None", 'Mild', 'Moderate', 'Severe', 'G. Atrophy'))

# par(mfrow = c(1,3))
# boxplot(DEFA1.A3.CN ~ DM6A_01_LABEL, data = rva1a3_array,
#         xlab = "DM6A_01", ylab = "DEFA1.A3.CN", 
#         notch = T, col = rainbow(5))
# boxplot(DEFA1.A3.CN ~ DM6A_13_LABEL, data = rva1a3_array, 
#         xlab = "DM6A_13", ylab = "DEFA1.A3.CN", 
#         notch = T, col = rainbow(5))
# boxplot(DEFA1.A3.CN ~ dtDM6A, data = rva1a3_array, 
#         xlab = "dtDM6A", ylab = "DEFA1.A3.CN", 
#         notch = T, col = rainbow(5))

va <- c("DM6A_01_LABEL", "DM6A_13_LABEL", "dtDM6A")

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

```

#### Scarring for left side
```{r cor-DMSA-left, fig.height = 4, fig.width = 14}
rva1a3_array$dtDM6B = (unclass(rva1a3_array$DM6B_13) - unclass(rva1a3_array$DM6B_01))%>% as.factor

rva1a3_array$DM6B_01_LABEL = recode(rva1a3_array$DM6B_01, 
                             "'A' = 'None'; 
                              'B' = 'Mild';
                              'C' = 'Moderate';
                              'D' = 'Severe';
                              'E' = 'G. Atrophy'
                             ")
rva1a3_array$DM6B_01_LABEL = factor(rva1a3_array$DM6B_01_LABEL, c("None", 'Mild', 'Moderate', 'Severe', 'G. Atrophy'))

rva1a3_array$DM6B_13_LABEL = recode(rva1a3_array$DM6B_13, 
                             "'A' = 'None'; 
                              'B' = 'Mild';
                              'C' = 'Moderate';
                              'D' = 'Severe';
                              'E' = 'G. Atrophy'
                             ")
rva1a3_array$DM6B_13_LABEL = factor(rva1a3_array$DM6B_13_LABEL, c("None", 'Mild', 'Moderate', 'Severe', 'G. Atrophy'))


va <- c("DM6B_01_LABEL", "DM6B_13_LABEL", "dtDM6B")

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))
```

#### Worst Scarring
```{r cor-Worst Scarring, fig.height = 4, fig.width = 14}
rva1a3_array$dtWORST_SCARRING = (unclass(rva1a3_array$WORST_SCARRING1301) - unclass(rva1a3_array$WORST_SCARRING0101))%>% as.factor

rva1a3_array$WORST_SCARRING0101_LABEL = recode(rva1a3_array$WORST_SCARRING0101, 
                             "'A' = 'None'; 
                              'B' = 'Mild';
                              'C' = 'Moderate';
                              'D' = 'Severe';
                              'E' = 'G. Atrophy'
                             ")
rva1a3_array$WORST_SCARRING0101_LABEL = factor(rva1a3_array$WORST_SCARRING0101_LABEL, c("None", 'Mild', 'Moderate', 'Severe', 'G. Atrophy'))

rva1a3_array$WORST_SCARRING1301_LABEL = recode(rva1a3_array$WORST_SCARRING1301, 
                             "'A' = 'None'; 
                              'B' = 'Mild';
                              'C' = 'Moderate';
                              'D' = 'Severe';
                              'E' = 'G. Atrophy'
                             ")
rva1a3_array$WORST_SCARRING1301_LABEL = factor(rva1a3_array$WORST_SCARRING1301_LABEL, c("None", 'Mild', 'Moderate', 'Severe', 'G. Atrophy'))

va <- c("WORST_SCARRING0101_LABEL", "WORST_SCARRING1301_LABEL", "dtWORST_SCARRING")

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))
```

#### Side with Worst Scarring
```{r cor-Side with Worst Scarring, fig.height = 4, fig.width = 14}
# rva1a3_array$WORST_SCARRING_SIDE1301_ = recode(rva1a3_array$WORST_SCARRING_SIDE1301, "'B' = NA; 'N' = NA")
# rva1a3_array$WORST_SCARRING_SIDE0101_ = recode(rva1a3_array$WORST_SCARRING_SIDE0101, "'B' = NA; 'N' = NA")

rva1a3_array$dtWORST_SCARRING_SIDE = unclass(rva1a3_array$WORST_SCARRING_SIDE1301) - unclass(rva1a3_array$WORST_SCARRING_SIDE0101)

rva1a3_array$dtWORST_SCARRING_SIDE_LABEL = recode(rva1a3_array$dtWORST_SCARRING_SIDE, 
                             " 0 = 'No Change'; 
                               1 = 'Change';
                               2 = 'Change';
                              -1 = 'Change'
                             ")

va <- c("WORST_SCARRING_SIDE0101", "WORST_SCARRING_SIDE1301", "dtWORST_SCARRING_SIDE_LABEL")

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

```

#### New Scar
```{r cor-New Scar, fig.height = 4, fig.width = 8}
rva1a3_array$SCAR_NEW04_LABEL = recode(rva1a3_array$SCAR_NEW04, " 0 = 'No'; 1 = 'Yes'")

va <- c("SCAR_NEW04_LABEL")

lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p1

lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p2
p = list()
p = c(p1, p2)
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))
```

### Grade and laterality (left/right/both) of vesicoureteral reflux
#### Highest grade of reflux for left ureter
```{r cor-VR-L, fig.height = 4, fig.width = 14}
rva1a3_array$dtVR_3L = as.factor(unclass(rva1a3_array$VR_3L_1301) - unclass(rva1a3_array$VR_3L_0101))

va <- c("VR_3L_0101", "VR_3L_1301", "dtVR_3L")

rva1a3_array$VR_3L_0101 = as.factor(rva1a3_array$VR_3L_0101)
rva1a3_array$VR_3L_1301 = as.factor(rva1a3_array$VR_3L_1301)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

```

#### Highest grade of reflux for right ureter
```{r cor-VR-R, fig.height = 4, fig.width = 14}
rva1a3_array$dtVR_3R = as.factor(unclass(rva1a3_array$VR_3R_1301) - unclass(rva1a3_array$VR_3R_0101))

va <- c("VR_3R_0101", "VR_3R_1301", "dtVR_3R")

rva1a3_array$VR_3R_0101 = as.factor(rva1a3_array$VR_3R_0101)
rva1a3_array$VR_3R_1301 = as.factor(rva1a3_array$VR_3R_1301)


p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

```

#### Highest Grade of reflux between both ureters
```{r cor-HIGHEST_REFLUX, fig.height = 4, fig.width = 14, eval = T}
rva1a3_array$dtHIGHEST_REFLUX = as.factor(unclass(rva1a3_array$HIGHEST_REFLUX1301) - unclass(rva1a3_array$HIGHEST_REFLUX0101))

rva1a3_array$HIGHEST_REFLUX0101_LABEL = recode(rva1a3_array$HIGHEST_REFLUX0101, 
                             " 0 = 'None'; 
                               1 = 'I';
                               2 = 'II';
                               3 = 'III';
                               4 = 'IV';
                               5 = 'V'
                             ")
rva1a3_array$HIGHEST_REFLUX1301_LABEL = recode(rva1a3_array$HIGHEST_REFLUX1301, 
                             " 0 = 'None'; 
                               1 = 'I';
                               2 = 'II';
                               3 = 'III';
                               4 = 'IV';
                               5 = 'V'
                             ")

va <- c("HIGHEST_REFLUX0101_LABEL", "HIGHEST_REFLUX1301_LABEL", "dtHIGHEST_REFLUX")

rva1a3_array$HIGHEST_REFLUX0101_LABEL = as.factor(rva1a3_array$HIGHEST_REFLUX0101_LABEL)
rva1a3_array$HIGHEST_REFLUX1301_LABEL = as.factor(rva1a3_array$HIGHEST_REFLUX1301_LABEL)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) & (rva1a3_array[va[i]] != "NA"), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

```

#### Side with highest grade of reflux between both ureters
```{r cor-HIGHEST_REFLUX_SIDE, fig.height = 4, fig.width = 14, eval = T}
rva1a3_array$dtHIGHEST_REFLUX_SIDE = as.factor(unclass(rva1a3_array$HIGHEST_REFLUX_SIDE1301) - unclass(rva1a3_array$HIGHEST_REFLUX_SIDE0101))

va <- c("HIGHEST_REFLUX_SIDE0101", "HIGHEST_REFLUX_SIDE1301", "dtHIGHEST_REFLUX_SIDE")

rva1a3_array$HIGHEST_REFLUX_SIDE0101 = as.factor(rva1a3_array$HIGHEST_REFLUX_SIDE0101)
rva1a3_array$HIGHEST_REFLUX_SIDE1301 = as.factor(rva1a3_array$HIGHEST_REFLUX_SIDE1301)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]), ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))
```

#### VUR lateral
```{r cor-VUR_LATERAL, fig.height = 4, fig.width = 14}
rva1a3_array$dtVUR_LATERAL = as.factor(unclass(rva1a3_array$VUR_LATERAL1301) - unclass(rva1a3_array$VUR_LATERAL0101))

va <- c("VUR_LATERAL0101", "VUR_LATERAL1301", "dtVUR_LATERAL")

rva1a3_array$VUR_LATERAL0101 = as.factor(rva1a3_array$VUR_LATERAL0101)
rva1a3_array$VUR_LATERAL1301 = as.factor(rva1a3_array$VUR_LATERAL1301)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))
```

### Number of UTI’s
```{r cor-PRIORUTI, fig.height = 4, fig.width = 14}
va <- c("PRIORUTI0101", "NUM_UTI01")
rva1a3_array$PRIORUTI0101 = as.factor(rva1a3_array$PRIORUTI0101)
rva1a3_array$NUM_UTI01 = as.factor(rva1a3_array$NUM_UTI01)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))
```

### Fevers with each episode
```{r cor-TYPE0103, fig.height = 4, fig.width = 14}
va <- c("UTI_TYPE0103")
rva1a3_array$UTI_TYPE0103 = as.factor(rva1a3_array$UTI_TYPE0103)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p[1]

lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p[2]
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))
```

### Type of Bacteria in each UTI 
#### Number of organisms present for the index UTI
```{r cor-NUMORG0101, fig.height = 4, fig.width = 12}
va <- c("NUMORG0101")
rva1a3_array$NUMORG0101 = as.factor(rva1a3_array$NUMORG0101)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p[1]

lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p[2]
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))
```

#### Primary and secondary species for the index UTI
```{r cor-SPECIES0101, fig.height = 4, fig.width = 12, eval = T}
va <- c("PORG_SPECIES0101", "SORG_SPECIES0101")
rva1a3_array$PORG_SPECIES0101 = as.factor(rva1a3_array$PORG_SPECIES0101)
rva1a3_array$SORG_SPECIES0101 = as.factor(rva1a3_array$SORG_SPECIES0101)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))

p = list()
lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))
```

#### Type of bacteria in first F/S UTI 
```{r cor-USRORG13A01, fig.height = 4, fig.width = 12}
va <- c("USRORG13A01")
rva1a3_array$USRORG13A01 = as.factor(rva1a3_array$USRORG13A01)

p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p[1]

lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p[2]
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))
```

### Sensitivities of Bacteria for first F/S UTI 
```{r cor-URINE_RES07, fig.height = 4, fig.width = 12}
rva1a3_array$URINE_RES07 = as.factor(rva1a3_array$URINE_RES07)
rva1a3_array$URINE_RES07_LABEL = recode(rva1a3_array$URINE_RES07, 
                             "'R' = 'Resistant'; 
                              'S' = 'Sensitive'
                             ")
va <- c("URINE_RES07_LABEL")
p = list()
lapply(seq_along(va), function(i) plt(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) & rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p[1]

lapply(seq_along(va), function(i) plt_point(df = rva1a3_array[!is.na(rva1a3_array[va[i]]) &rva1a3_array[va[i]] != "NA", ], x = va[i], y = "DEFA1.A3.CN")) -> p[2]
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))
```



