---
title: "RIVUR"
output: html_document
---

```{r setting, message = FALSE, echo=FALSE}
# xiao
# shi

# output:
#   knitrBootstrap::bootstrap_document:
#     theme.chooser: T
#     highlight.chooser: FALSE
#     menu: F
#     title: "IGLL5 report"
library(xlsx)
library(car)
library(knitr)
library(xtable)
library(dplyr)
library(ggplot2)
library(reshape2)
library(magrittr)
library(gridExtra)
library(gmodels)
library(psych)
library(tabplot)
opts_chunk$set(dev=c("svg"), 
              fig.height = 6, fig.width = 8)
opts_chunk$set(fig.show="hold")
opts_chunk$set(warning=F, message = FALSE, echo=F, results='asis')
opts_chunk$set(bootstrap.thumbnail.size='col-md-7', 
               bootstrap.thumbnail = T,
               bootstrap.panel = T)

# source("/Users/DL/Documents/R project/Memphis - Copy Number Variation/Functions/myFunction.R")

science_theme = theme(panel.grid.major = element_line(size = 0.4, color = "grey"),
                      axis.line = element_line(size = 0.5, color = "black"), 
                      legend.position = "none", 
#                       legend.position = c(0.85, 0.85),
                      plot.title = element_text(lineheight=.8, size = 10,  face="bold"),
                      text = element_text(size = 14))   
```

```{r data_load_preprocessing, cache=T, message = FALSE, echo=F, results='asis'}

# rva1a3 <- read.xlsx2("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/RIVUR data/RIVUR Spreadsheets/RV111201 A1A3.xls", sheetIndex = 1, header = T, stringsAsFactors = F) %>% tbl_df

rva1a3_array <- read.xlsx("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/RIVUR data/RIVUR Spreadsheets/RV111201 A1A3 and Array Master Factors.xls", sheetIndex = 1, header = T, stringsAsFactors = T) %>% tbl_df
names(rva1a3_array) = toupper(names(rva1a3_array))

# str(rva1a3)
# dim(rva1a3)
# names(rva1a3)
# names(rva1a3_array)
# IQR(rva1a3_array$DEFA1.A3.CN, na.rm = T)
# prop.table(table(rva1a3_array$DEFA1.A3.CN))
# quantile(rva1a3_array$DEFA1.A3.CN, na.rm = T, probs = 0.01)
# boxplot(rva1a3_array$DEFA1.A3.CN, notch = T, varwidth = T)
# 
# CrossTable(x = rva1a3_array$AGE0101, y = rva1a3_array$RACE0102)

pairs.panels(rva1a3_array[c("AGE0101","RACE0102","SEX0101", "DEFA1.A3.CN")])

```

## Data summary
```{r summary - table}
# rva1a3_array %>% group_by(ETHNIC0101, SEX0101) %>%
#         summarize(mean(DEFA1.A3.CN), n()) -> t1
# 
rva1a3_array %>% group_by(RACE0102) %>%
        summarize(DEFA1A3.mean = mean(DEFA1.A3.CN), Nbs = n()) -> t2
# 
# rva1a3_array %>% group_by(RaceEth, SEX0101) %>%
#         summarize(mean(DEFA1.A3.CN), n()) -> t3

# kable(t1)
# kable(t2)
# kable(t3)

```

```{r summary - plot}
par(mfrow = c(2,2))
hist(rva1a3_array$AGE0101, xlab = "Age")
hist(rva1a3_array$RACE0102, breaks = 20, xlab = "Race")
plot(factor(rva1a3_array$SEX0101), xlab = "Sex")
hist(rva1a3_array$DEFA1.A3.CN, xlab = "DEFA1A3.CN")
```

## Correlation
### Race & Age 
```{r cor, fig.height = 4, fig.width = 10}
rva1a3_array$RACE0102_EXP = recode(rva1a3_array$RACE0102, 
                             "1 = 'White'; 
                              2 = 'Black';
                              3 = 'Asian';
                              4 = 'Hawaiian/Pacific Islander ';
                              5 = 'American Indian/Alaskan';
                              6 = 'Other';
                              7 = 'Mixed';
                              8 = 'Missing'
                             ")
par(mfrow = c(1,2))
boxplot(DEFA1.A3.CN ~ RACE0102_EXP, data = rva1a3_array, 
        xlab = "Race", ylab = "DEFA1.A3.CN",
        col = rainbow(7),
        notch = T)
boxplot(DEFA1.A3.CN ~ SEX0101, data = rva1a3_array, 
        xlab = "Sex", ylab = "DEFA1.A3.CN",
        notch = T, varwidth = F)

```

> Among all the races recoded, Asian population tends to have highest copy number of DEFA1A3 with median copy number value of DEFA1A3 at 7.

### Bladder and bowel movement dysfunction
```{r cor2, fig.height = 4, fig.width = 10}
rva1a3_array$dtBBD = rva1a3_array$BBD1302 - rva1a3_array$BBD0102
rva1a3_array$dtBBD_EXP = recode(rva1a3_array$dtBBD, 
                             "1 = 'Worse'; 
                              0 = 'No Change';
                             -1 = 'Better'")

par(mfrow = c(1,3))
boxplot(DEFA1.A3.CN ~ BBD0102, data = rva1a3_array, 
        xlab = "BBD0102", ylab = "DEFA1.A3.CN")
boxplot(DEFA1.A3.CN ~ BBD1302, data = rva1a3_array, 
        xlab = "BBD1302", ylab = "DEFA1.A3.CN")
boxplot(DEFA1.A3.CN ~ dtBBD_EXP, data = rva1a3_array, 
        xlab = "dtBBD_EXP", ylab = "DEFA1.A3.CN",
        col = rainbow(3))
```


> Higher copy number of DEFA1A3 appears to be associated with better dtBBD score (changing from socre 1 to 0, indicative of BBD getting better) two years after intial recruitment.

```{r ddBBD by TXGROUP, eval = F}
ggplot(rva1a3_array, aes(x = dtBBD_EXP, y = DEFA1.A3.CN, fill = dtBBD_EXP)) +
        geom_boxplot() +
        geom_point(position = "jitter")+
        scale_y_discrete(limits = c(3:14)) +
        facet_grid(.~TXGROUP) +
        theme_bw() +
        science_theme +
        scale_fill_brewer(palette = "Set3")
# 
# rva1a3_array %>% 
#         group_by(dtBBD_EXP) %>%
#         summarise(mean(DEFA1.A3.CN, na.rm = T), n())

```

### TF02
```{r cor-TF02, fig.height = 4, fig.width = 12}
rva1a3_array$TF02_LABLE = recode(rva1a3_array$TF02, 
                             "1 = 'Treatment Failure'; 
                              0 = 'No Treatment Failure'
                             ")

# par(mfrow = c(1,1))
# boxplot(DEFA1.A3.CN ~ TF02_LABLE, data = rva1a3_array, 
#         xlab = "TF02", ylab = "DEFA1.A3.CN")

ggplot(rva1a3_array, aes(x = TF02_LABLE, y = DEFA1.A3.CN, fill =TF02_LABLE)) +
        geom_boxplot() +
        geom_point(position = "jitter")+
        scale_x_discrete() +
        facet_grid(.~TXGROUP) +
        theme_bw() +
        science_theme 


```

```{r cor-TF02 table, eval = F}
rva1a3_array %>% 
        group_by(TF02_LABLE, TXGROUP) %>%
        summarise(DEFA1A3.median = median(DEFA1.A3.CN, na.rm = T), Nbs = n()) %>% 
        kable(align = "l")
```

### DVQ SCORE
```{r cor-DVQSCORE, fig.height = 4, fig.width = 12}
rva1a3_array$dtDVQSCORE = rva1a3_array$DVQSCORE1304 - rva1a3_array$DVQSCORE0104

# par(mfrow = c(1,3))
# plot(DVQSCORE0104 ~ DEFA1.A3.CN, data = rva1a3_array, 
#         ylab = "DVQSCORE0104", xlab = "DEFA1.A3.CN")
# plot(DVQSCORE1304 ~ DEFA1.A3.CN, data = rva1a3_array, 
#         ylab = "DVQSCORE1304", xlab = "DEFA1.A3.CN")
# plot(dtDVQSCORE ~ DEFA1.A3.CN, data = rva1a3_array, 
#         ylab = "dtDVQSCORE", xlab = "DEFA1.A3.CN")

# lm(DVQSCORE1304 ~ DEFA1.A3.CN, data = rva1a3_array)%>%summary

ggplot(rva1a3_array[!is.na(rva1a3_array$DEFA1.A3.CN), ], aes(x = factor(DEFA1.A3.CN), y = DVQSCORE0104)) +
#         geom_boxplot() +
        geom_point(position = "")+
        geom_smooth(method = "lm") +
#         xlim = c(3, 14) +
#         scale_x_discrete() +
#         facet_grid(.~TXGROUP) +
        theme_bw() +
        science_theme -> p1

ggplot(rva1a3_array[!is.na(rva1a3_array$DEFA1.A3.CN), ], aes(x = factor(DEFA1.A3.CN), y = DVQSCORE1304)) +
#         geom_boxplot() +
        geom_point(position = "", fill = "black", col = "blue")+
        geom_smooth(method = "lm") +
#         xlim = c(3, 14) +
#         scale_x_discrete() +
#         facet_grid(.~TXGROUP) +
        theme_bw() +
        science_theme -> p2

ggplot(rva1a3_array[!is.na(rva1a3_array$DEFA1.A3.CN), ], aes(x = factor(DEFA1.A3.CN), y = dtDVQSCORE)) +
#         geom_boxplot() +
        geom_point(position = "", fill = "black", col = "blue")+
        geom_smooth(method = "lm") +
#         xlim = c(3, 14) +
#         scale_x_discrete() +
#         facet_grid(.~TXGROUP) +
        theme_bw() +
        science_theme -> p3

plot = list()
plot = list(p1, p2, p3)
do.call(grid.arrange, c(plot, list(nrow = 1, ncol =3)))

```

### Chronic constipation
```{r cor-DVQSCORE, fig.height = 4, fig.width = 10}
rva1a3_array$dtCHR_CONST_LABEL = unlist(rva1a3_array$CHR_CONST1302) - rva1a3_array$CHR_CONST0102

par(mfrow = c(1,3))
boxplot(DEFA1.A3.CN ~ CHR_CONST0102, data = rva1a3_array, 
        xlab = "CHR_CONST0102", ylab = "DEFA1.A3.CN", 
        notch = T, col = rainbow(2))
boxplot(DEFA1.A3.CN ~ CHR_CONST1302, data = rva1a3_array, 
        xlab = "CHR_CONST1302", ylab = "DEFA1.A3.CN",
        notch = T)
boxplot(DEFA1.A3.CN ~ dtBBD_EXP, data = rva1a3_array, 
        xlab = "dtBBD_EXP", ylab = "DEFA1.A3.CN",
        col = rainbow(3))

```








## Caucasian Female
```{r C-F, eval=F}
cf <- filter(rva1a3_array, RACE0102 == 1, SEX0101 == "F")



cf %>% group_by(PRIORUTI0101) %>%
        summarize(mean(DEFA1.A3.CN), n())
cf %>% group_by(NUM_UTI01) %>%
        summarize(mean(DEFA1.A3.CN), n())
cf$DEFA1.A3.CN = as.numeric(cf$DEFA1.A3.CN)

par(mfrow = c(2,2))
plot(cf$DEFA1.A3.CN ~ cf$PRIORUTI0101)
plot(DEFA1.A3.CN ~ AGE0101, data = cf)
plot(DEFA1.A3.CN ~ NUM_UTI01, data = cf)
```

```{r plot, eval=F}
ggplot(cf, aes(x = NUM_UTI01, y = DEFA1.A3.CN)) + 
        geom_boxplot() +
        geom_point(position = "jitter")+
        theme_bw() +
        science_theme

# lm(DEFA1.A3.CN ~ NUM_UTI01, data = cf) %>% summary

ggplot(cf, aes(x = as.factor(DVQSCORE0104), y = as.numeric(DEFA1.A3.CN))) + 
        geom_boxplot() +
        geom_point(position = "jitter")+
        theme_bw() +
        science_theme
        
ggplot(cf, aes(x = as.factor(URINE_RES07), y = as.numeric(DEFA1.A3.CN))) + 
        geom_boxplot() +
        geom_point(position = "jitter")+
        theme_bw() +
        science_theme

ggplot(cf, aes(x = as.factor(USRORG13A01), y = as.numeric(DEFA1.A3.CN))) + 
        geom_boxplot(aes(fill = USRORG13A01)) +
        geom_point(position = "jitter")+
        theme_classic() +
        science_theme

        
```


```{r vesicoureteral reflux, eval=F}
names(cf) = toupper(names(cf))
cf %>% mutate(dtVR_3L = as.numeric(VR_3L_1301) - as.numeric(VR_3L_0101),
              dtVR_3R = as.numeric(VR_3R_1301) - as.numeric(VR_3R_0101),
              dtHIGHEST_REFLUX = as.numeric(HIGHEST_REFLUX1301) - as.numeric(HIGHEST_REFLUX0101),
              dtHIGHEST_REFLUX_SIDE = ifelse(HIGHEST_REFLUX_SIDE0101==HIGHEST_REFLUX_SIDE1301, 'NO', "YES"),
              dtDVQSCORE = as.numeric(DVQSCORE1304) - as.numeric(DVQSCORE0104)
              ) %>%
        select(dtVR_3L : dtDVQSCORE, DEFA1.A3.CN, TXGROUP, SEX0101)  ->cf_prog

cf_prog %>% 
        ggplot(., aes(x = dtVR_3L, y = DEFA1.A3.CN)) +
        geom_point(position = "jitter") +
        geom_smooth(method = "lm") +
        facet_grid(.~TXGROUP) +
        theme_bw() +
        science_theme


ggplot(data = cf_prog, aes(y = DEFA1.A3.CN, x = dtDVQSCORE)) +  
        geom_point(position = "jitter") +
        geom_smooth(method = "lm") +
        facet_grid(.~TXGROUP) +
        theme_bw() +
        science_theme

# pl = list()
# plot <- lapply(seq_along(names(cf_prog)), function(i) {
#         var = names(cf_prog)[i]
#         
#         pl <- ggplot(data = cf_prog, aes(y = DEFA1.A3.CN, x = var)) +  
#                 geom_point(position = "jitter") +
#                 geom_smooth(method = "lm") +
#                 facet_grid(.~TXGROUP) +
#                 theme_bw() +
#                 science_theme
#         
#         pl
# })
# 
# do.call(grid.arrange, c(plot, list(nrow = 4, ncol =2)))

```

```{r tblplot, eval=F}

```



