---
title: "RIVUR - IGLL5 association study"
output:
  html_document:
    theme: cerulean
---

```{r output, eval = F, echo = F}
output:
  knitrBootstrap::bootstrap_document:
    theme: default
    highlight: sunburst
    theme.chooser: TRUE
    highlight.chooser: TRUE
```

```{r setting, message = FALSE, echo=FALSE}
# output:
#   knitrBootstrap::bootstrap_document:
#     theme.chooser: T
#     highlight.chooser: FALSE
#     menu: F
#     title: "IGLL5 repor
library(agricolae)
library(xlsx)
library(car)
library(knitr)
# library(xtable)
library(dplyr)
library(ggplot2)
library(reshape2)
library(magrittr)
library(gridExtra)
# library(gmodels)
# library(psych)
# library(tabplot)
opts_chunk$set(dev=c("svg"), 
              fig.height = 4.5, fig.width = 15)
opts_chunk$set(fig.show="hold")
opts_chunk$set(warning=F, message = FALSE, echo=F, results='asis')
opts_chunk$set(bootstrap.thumbnail.size='col-md-12', 
               bootstrap.thumbnail = T,
               bootstrap.panel = T)

# source("/Users/DL/Documents/R project/Memphis - Copy Number Variation/Functions/myFunction.R")
 
```

```{r functions, echo=F}
science_theme = theme(panel.grid.major = element_line(size = 0.4, color = "grey"),
                      axis.line = element_line(size = 0.5, color = "black"), 
                      legend.position = "bottom", 
#                       legend.position = c(0.85, 0.85),
                      plot.title = element_text(lineheight=.8, size = 10,  face="bold"),
                      text = element_text(size = 14))  

plt_box <- function(df, y, x){
        ggplot(df, aes_string(y = y, x = x)) +
                geom_boxplot(aes_string(fill = x)) +
                scale_y_continuous() +
                scale_fill_brewer(palette = "Accent")+
                theme_bw() +
                science_theme
                
}

plt_prop <- function (data, x, fill) {
#         data = data[complete.cases(data),]
        TABLE_FUN = eval(parse(text = paste0("table(data$", x, ", data$", fill, ")"))) 
        data_prop = prop.table(TABLE_FUN,2) %>% data.frame
        data_prop = data_prop[complete.cases(data_prop),]
        names(data_prop) = c(x, fill, "Proportion")
        
        cat("\n",fill)
        table = as.data.frame.matrix(TABLE_FUN) %>% tbl_df
        table = table[colnames(table) != 'NA']
        kable(table)
        cat("\n")

        ggplot(data_prop, aes_string(x = x, y = "Proportion", fill = fill))+
                geom_bar(stat = "identity", col = "black", position = "dodge")+
                scale_x_discrete()+
                scale_fill_brewer(palette = "Accent")+
                theme_bw() + 
                science_theme 
}

plt_ecdf <- function (data, x, group) {
        ggplot(data, aes_string(x = x, col = group)) + 
                geom_line(stat = "ecdf", size = 1) +
#                 scale_x_discrete()+
                ylab("Cumulative Proportion") +
                scale_color_brewer(palette = "Accent")+
                theme_bw() + 
                science_theme
}

plt_triple <- function (data = rv, gene = "COPY.NBS.ROUND", va) {
        data = data[!is.na(data[va])&!is.na(data[gene])&data[gene] != 'NA'&data[va]!= 'NA', ]
        p = list()
        lapply(seq_along(va), function (i) plt_box(data, "DDCT.MEAN", va)) -> p[1]
        lapply(seq_along(va), function (i) plt_prop(data = data, x = gene, fill = va)) -> p[2]
        lapply(seq_along(va), function (i) plt_ecdf(data, gene, va)) -> p[3]
        do.call(grid.arrange, c(p, list(nrow = 1, ncol =3)))
}

plt <- function(df, x, y){
        df_l = "rv[!is.na(rv[x]) & (rv[x] != 'NA'), ]"
        
        pa <- paste0("(",df_l,"$",y,", ", df_l,"$",x)
        FUN_kruskal = paste0("kruskal", pa, ", group = F, console = F)")
        result_kruskal = eval(parse(text = FUN_kruskal))$comparison
        
        cat("\n",x)
        if (dim(result_kruskal[result_kruskal$pvalue < 0.05,])[1] != 0){
                kable(result_kruskal[result_kruskal$pvalue < 0.05,])
        }
        cat("\n")
        
        para <- paste0("(",df_l,"$",y,", ", df_l,"$",x, ")")
        FUN_TABLE <- paste0("table",  para)
        p.chisq = chisq.test(eval(parse(text = FUN_TABLE)))$p.value
        p.kruskal = kruskal.test(as.formula(paste0(y, "~", x)), data = df)$p.value
        p = p.kruskal
        print(p)
        
        if(p > 0.2 | p == "NaN" | !exists("p")) {
                ggplot(df, aes_string(y = y, x = x)) +
                        geom_boxplot() +
                        scale_y_continuous(breaks = 3:14) +
                        theme_bw() +
                        science_theme
        } else
                ggplot(df, aes_string(y = y, x = x)) +
                geom_boxplot(aes_string(fill = x)) +
                scale_y_continuous(breaks = 3:14) +
                theme_bw() +
                science_theme
        
        
}

plt_point <- function(df, x, y){
#         oneway_p = oneway.test(as.formula(paste0(y," ~ ",x)), data = df)$p.value
        df_l = "rv[!is.na(rv[x]) & (rv[x] != 'NA')&rv[!is.na(rv[y]) & (rv[y] != 'NA'), ]"
        para <- paste0("(",df_l,"$",y,", ", df_l,"$",x, ")")
        FUN_TABLE <- paste0("table",  para)
        p.chisq = chisq.test(eval(parse(text = FUN_TABLE)))$p.value
        p.kruskal = kruskal.test(as.formula(paste0(y, "~", x)), data = df)$p.value
        p = p.kruskal
#         print(p)
        if(p > 0.2| p == "NaN") {
                ggplot(df, aes_string(y = y, x = x)) +
                        geom_point(position = "") +
                        stat_sum(aes(size = ..n..)) +
                        scale_y_continuous(breaks = 3:14) +
                        scale_x_discrete() +
                        theme_bw() +
                        science_theme
        }else
                ggplot(df, aes_string(y = y, x = x)) +
                geom_point(position = "", col = "blue") +
                stat_sum(aes(size = ..n..), col = "blue") +
                scale_y_continuous(breaks = 3:14) +
                scale_x_discrete() +
                theme_bw() +
                science_theme
}

plt_s <- function(df, x, y){
        ggplot(df, aes_string(y = y, x = x)) +
        geom_boxplot() +
        scale_y_continuous(breaks = 3:14) +
        theme_bw() +
        science_theme
}

plt_point_s <- function(df, x, y){
        ggplot(df, aes_string(y = y, x = x)) +
        geom_point(position = "") +
        stat_sum(aes(size = ..n..)) +
        scale_y_continuous(breaks = 3:14) +
        scale_x_discrete() +
        theme_bw() +
        science_theme
}
```


```{r data_load_preprocessing, cache=T, message = FALSE, echo=F, results='asis'}

# rv <- read.xlsx("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/RIVUR data/RIVUR Spreadsheets/RV111201 A1A3 and Array Master Factors.xls", sheetIndex = 1, header = T, stringsAsFactors = T) %>% tbl_df

rv <- read.csv("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/IGLL5/Raw data/IGLL5-grand_table(cali = J).csv", header = T, stringsAsFactors = T) %>% tbl_df

sampleInfo = read.xlsx("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/RIVUR data/RIVUR Spreadsheets/RV111201 A1A3.xls", sheetIndex = 1, header = T, stringsAsFactors = T) %>% tbl_df

knum_ = sub("^ |-D$|A$|B$|-DNA-LCL| -$", "", sampleInfo$Knum.Original)
knum = sub("^ |-D$|A$|B$|-DNA-LCL| -$", "", knum_)
sampleInfo$knum = knum

rv = merge(rv, sampleInfo, by.x = "RUID", by.y = "knum", all = T)
names(rv) = toupper(names(rv))
rv = rv[rv$DDCT.SEM<0.5 & !is.na(rv$DDCT.MEAN), ]


rv$COPY.NBS.ROUND = recode(rv$COPY.NBS.ROUND, 
                             "-1 = 0")


rv$TXGROUP_LABEL = recode(rv$TXGROUP, 
                             "'A' = 'TMP/SMZ'; 
                              'P' = 'Placebo'
                             ")
rv$TF02_LABEL = recode(rv$TF02, 
                             "1 = 'Treatment Failure'; 
                              0 = 'No Treatment Failure'
                             ")
rv$RACE0102_LABEL = recode(rv$RACE0102, 
                             "1 = 'White'; 
                              2 = 'Black';
                              3 = 'Asian';
                              4 = 'Hawaiian/Pacific Islander ';
                              5 = 'American Indian/Alaskan';
                              6 = 'Other';
                              7 = 'Mixed';
                              8 = 'Missing'
                             ")

rv$dtCHR_CONST = unclass(rv$CHR_CONST1302) - unclass(rv$CHR_CONST0102)

rv$dtCHR_CONST_LABEL = recode(rv$dtCHR_CONST, 
                             "-1 = 'Better'; 
                               0 = 'No Change';
                               1 = 'Worse'
                             ")
# rv = filter(rv, RACE0102_LABEL == 'White', SEX0101 == "F", TXGROUP_LABEL == "TMP/SMZ")
rv = filter(rv, RACE0102_LABEL == 'White', TXGROUP_LABEL == "Placebo")
```
## Data summary
```{r summary - plot, fig.height = 7, fig.width = 10, eval = T}
par(mfrow = c(2,3))
hist(rv$AGE0101, xlab = "Age",breaks = 20, main = "")
plot(as.factor(rv$RACE0102_LABEL), breaks = 7, xlab = "Race", main = "")
plot(factor(rv$SEX0101), xlab = "Sex", main = "")
hist(rv$COPY.NBS.ROUND, xlab = "IGLL5.Copy.Nbs", breaks = 12, main = "")
plot(rv$TXGROUP_LABEL, xlab = "Treatment group assignment")
plot(as.factor(rv$TF02_LABEL), xlab = "Treatment failure")
```

## Correlation
### Gender
```{r sex}
va <- c("SEX0101")
lapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible
```


```{r ### Race cor - Race, eval = F}
rv$RACE0102_LABEL = recode(rv$RACE0102, 
                             "1 = 'White'; 
                              2 = 'Black';
                              3 = 'Asian';
                              4 = 'Hawaiian/Pacific Islander ';
                              5 = 'American Indian/Alaskan';
                              6 = 'Other';
                              7 = 'Mixed';
                              8 = 'Missing'
                             ")
rv$RACE0102_LABEL = as.factor(rv$RACE0102_LABEL)
va <- c("RACE0102_LABEL", "SEX0101")

p = list()
lapply(seq_along(va), function(i) plt_s(df = rv[!is.na(rv[va[i]]), ], x = va[i], y = "COPY.NBS.ROUND")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))

p = list()
lapply(seq_along(va), function(i) plt_point_s(df = rv[!is.na(rv[va[i]]), ], x = va[i], y = "COPY.NBS.ROUND")) -> p
do.call(grid.arrange, c(p, list(nrow = 1, ncol =2)))

# par(mfrow = c(1,2))
# boxplot(DEFA1.A3.CN ~ RACE0102_LABEL, data = rva1a3_array, 
#         xlab = "Race", ylab = "Copy.Nbs",
#         col = rainbow(7),
#         notch = T)
# boxplot(DEFA1.A3.CN ~ SEX0101, data = rva1a3_array, 
#         xlab = "Sex", ylab = "Copy.Nbs",
#         notch = T, varwidth = F)

```

### Chronic constipation
```{r dtCHR_CONST_LABEL}
va <- c("CHR_CONST0102", "CHR_CONST1302", "dtCHR_CONST_LABEL")
lapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible
```

### Grade and laterality (left/right/both) of vesicoureteral reflux
#### Highest grade of reflux for left ureter
```{r VR_3L}
rv$VR_3L_1301_LABEL = recode(rv$VR_3L_1301, 
                             " 0 = NA; 
                               1:2 = 'Low';
                               3:5 = 'High'
                             ")
rv$VR_3L_0101_LABEL = recode(rv$VR_3L_0101, 
                             " 0 = NA; 
                               1:2 = 'Low';
                               3:5 = 'High'
                             ")

rv$dtVR_3L = rv$VR_3L_1301-rv$VR_3L_0101
rv$dtVR_3L_LABEL = recode(rv$dtVR_3L, 
                             " -5:-1 = 'Better'; 
                               0 = 'No Change';
                               1:hi = 'Worse'
                             ")

# unclass(factor(rv$VR_3L_1301_LABEL, levels = c("Low", "High")))

va <- c("VR_3L_0101_LABEL", "VR_3L_1301_LABEL", "dtVR_3L_LABEL")
sapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible

```

#### Highest grade of reflux for right ureter
```{r VR_3R}
rv$VR_3R_1301_LABEL = recode(rv$VR_3R_1301, 
                             " 0 = NA; 
                               1:2 = 'Low';
                               3:5 = 'High'
                             ")
rv$VR_3R_0101_LABEL = recode(rv$VR_3R_0101, 
                             " 0 = NA; 
                               1:2 = 'Low';
                               3:5 = 'High'
                             ")
rv$dtVR_3R = rv$VR_3R_1301-rv$VR_3R_0101
rv$dtVR_3R_LABEL = recode(rv$dtVR_3R, 
                             " -5:-1 = 'Better'; 
                               0 = 'No Change';
                               1:hi = 'Worse'
                             ")
va <- c("VR_3R_0101_LABEL", "VR_3R_1301_LABEL", "dtVR_3R_LABEL")
sapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible

```

#### Highest Grade of reflux between both ureters
```{r cor-HIGHEST_REFLUX}
rv$dtHIGHEST_REFLUX = as.factor(unclass(rv$HIGHEST_REFLUX1301) - unclass(rv$HIGHEST_REFLUX0101))

rv$HIGHEST_REFLUX0101_LABEL = recode(rv$HIGHEST_REFLUX0101, 
                             " 0 = 'None'; 
                               1 = 'I';
                               2 = 'II';
                               3 = 'III';
                               4 = 'IV';
                               5 = 'V'
                             ")
rv$HIGHEST_REFLUX1301_LABEL = recode(rv$HIGHEST_REFLUX1301, 
                             " 0 = 'None'; 
                               1 = 'I';
                               2 = 'II';
                               3 = 'III';
                               4 = 'IV';
                               5 = 'V'
                             ")

# 
# rv$HIGHEST_REFLUX0101_LABEL = recode(rv$HIGHEST_REFLUX0101, 
#                              " 0 = NA; 
#                                1:2 = 'Low';
#                                3:5 = 'High'
#                              ")
# rv$HIGHEST_REFLUX1301_LABEL = recode(rv$HIGHEST_REFLUX1301, 
#                              " 0 = NA; 
#                                1:2 = 'Low';
#                                3:5 = 'High'
#                              ")
# 
# rv$dtHIGHEST_REFLUX = rv$HIGHEST_REFLUX1301-rv$HIGHEST_REFLUX0101
# rv$dtHIGHEST_REFLUX_LABEL = recode(rv$dtHIGHEST_REFLUX, 
#                             " -5:-1 = 'Better'; 
#                                0 = 'No Change';
#                                1:hi = 'Worse'
#                              ")


va <- c("HIGHEST_REFLUX0101_LABEL", "HIGHEST_REFLUX1301_LABEL", "dtHIGHEST_REFLUX")
sapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible
# rv$HIGHEST_REFLUX0101_LABEL = as.factor(rv$HIGHEST_REFLUX0101_LABEL)
# rv$HIGHEST_REFLUX1301_LABEL = as.factor(rv$HIGHEST_REFLUX1301_LABEL)


```


#### Side with highest grade of reflux between both ureters
```{r cor-HIGHEST_REFLUX_SIDE}


rv$HIGHEST_REFLUX_SIDE1301_recode = recode(rv$HIGHEST_REFLUX_SIDE1301, 
                            " 'Left' = 1; 
                              'Right' = 2; 
                              'Both' = 4; 
                             ") %>% as.numeric

rv$HIGHEST_REFLUX_SIDE0101_recode = recode(rv$HIGHEST_REFLUX_SIDE0101, 
                            " 'Left' = 1; 
                              'Right' = 2; 
                              'Both' = 4; 
                             ") %>% as.numeric
rv$dtHIGHEST_REFLUX_SIDE_recode = rv$HIGHEST_REFLUX_SIDE1301_recode - rv$HIGHEST_REFLUX_SIDE0101_recode

rv$dtHIGHEST_REFLUX_SIDE_LABEL = recode(rv$dtHIGHEST_REFLUX_SIDE_recode, 
                                        " 1 = 'L-R'; 
                                         -1 = 'R-L'; 
                                          3 = 'L-B'; 
                                         -3 = 'B-L'; 
                                          2 = 'R-B'; 
                                         -2 = 'B-R';
                                          0 = 'No Change'
                                        ") %>% as.factor

va <- c("HIGHEST_REFLUX_SIDE0101", "HIGHEST_REFLUX_SIDE1301", "dtHIGHEST_REFLUX_SIDE_LABEL")
sapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible

# rv$HIGHEST_REFLUX_SIDE0101 = as.factor(rv$HIGHEST_REFLUX_SIDE0101)
# rv$HIGHEST_REFLUX_SIDE1301 = as.factor(rv$HIGHEST_REFLUX_SIDE1301)

```

#### VUR lateral
```{r cor-VUR_LATERAL}
rv$dtVUR_LATERAL = as.factor(unclass(rv$VUR_LATERAL1301) - unclass(rv$VUR_LATERAL0101))

va <- c("VUR_LATERAL0101", "VUR_LATERAL1301", "dtVUR_LATERAL")
sapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible
```

### Number of UTI’s
```{r cor-PRIORUTI, eval=T}
rv$PRIORUTI0101 = as.factor(rv$PRIORUTI0101)
rv$NUM_UTI01 = as.factor(rv$NUM_UTI01)
va <- c("PRIORUTI0101", "NUM_UTI01")
sapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible
```

### DMSA scan results
#### New Scar
```{r cor-New Scar}
rv$SCAR_NEW04_LABEL = recode(rv$SCAR_NEW04, " 0 = 'No'; 1 = 'Yes'")

va <- c("SCAR_NEW04_LABEL")
sapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible

```

#### Worst Scarring
```{r cor-Worst Scarring}
rv$dtWORST_SCARRING = (unclass(rv$WORST_SCARRING1301) - unclass(rv$WORST_SCARRING0101))%>% as.factor

rv$WORST_SCARRING0101_LABEL = recode(rv$WORST_SCARRING0101, 
                             "'A' = 'None'; 
                              'B' = 'Mild';
                              'C' = 'Moderate';
                              'D' = 'Severe';
                              'E' = 'G. Atrophy'
                             ")
rv$WORST_SCARRING0101_LABEL = factor(rv$WORST_SCARRING0101_LABEL, c("None", 'Mild', 'Moderate', 'Severe', 'G. Atrophy'))

rv$WORST_SCARRING1301_LABEL = recode(rv$WORST_SCARRING1301, 
                             "'A' = 'None'; 
                              'B' = 'Mild';
                              'C' = 'Moderate';
                              'D' = 'Severe';
                              'E' = 'G. Atrophy'
                             ")
rv$WORST_SCARRING1301_LABEL = factor(rv$WORST_SCARRING1301_LABEL, c("None", 'Mild', 'Moderate', 'Severe', 'G. Atrophy'))

va <- c("WORST_SCARRING0101_LABEL", "WORST_SCARRING1301_LABEL", "dtWORST_SCARRING")
sapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible

```

### Bladder and bowel movement dysfunction 
```{r cor - BBD}
rv$dtBBD = (rv$BBD1302 - rv$BBD0102)
rv$dtBBD_LABEL = recode(rv$dtBBD, 
                             "1 = 'Worse'; 
                              0 = 'No Change';
                             -1 = 'Better'")

rv$BBD0102 = as.factor(rv$BBD0102)
rv$BBD1302 = as.factor(rv$BBD1302)
rv$dtBBD_LABEL = as.factor(rv$dtBBD_LABEL)

va <- c("BBD0102", "BBD1302", "dtBBD_LABEL")
sapply(seq_along(va), function(i) plt_triple(va = va[i])) %>% invisible
```

