---
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
  word_document: default
---
Copy number variation of DEFA1A3
========================================================

```{r table_setup, echo=FALSE, eval=F}
tn = local({
  i = 0
  function(x) {
    i <<- i + 1
    paste('\n Table ', i, ': ', x, sep = '')
    # The : before Table tells pandoc to wrap your caption in <caption></caption>
  }
})
knit_hooks$set(tab.cap = function(before, options, envir) {
  if(!before)
    tn(options$tab.cap)
})
default_output_hook = knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == F)  
    x
  else
    default_output_hook(x,options)
})
```

```{r fig_setup, include=FALSE, eval = F}
fn = local({
  i = 0
  function(x) {
    i <<- i + 1
    paste('Figure ', i, ': ', x, sep = '')
  }
})

```

```{r read-chunk, message = FALSE, echo=FALSE}
library(knitr)
library(xtable)
library(dplyr)
library(ggplot2)
library(reshape2)
read_chunk("/Users/DL/Documents/R project/Memphis - Copy Number Variation/copyTyping.r")
# opts_chunk$set(dev=c("png"), 
#                dev.args=list(type="cairo"),
#                dpi =300, fig.height = 4, fig.width = 8)
# opts_chunk$set(fig_path = "/Users/DL/Documents/R%20project/Memphis%20-%20Copy%20Number%20Variation/Copy%20typing%20report/figure/")
# opts_chunk$set(dev=c("pdf"), 
#               fig.height =6, fig.width = 7)
opts_chunk$set(dev=c("pdf"), 
              fig.height = 5, fig.width = 5)
# opts_chunk$set(dev="tiff", 
#                dev.args=list(compression="lzw"),
#                dpi=300)
opts_chunk$set(fig.show="hold")
opts_chunk$set(echo = F, warning = F)
```


```{r data_load, cache=FALSE, message = FALSE, echo=F, results='asis'}
data <- read.table("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/RT-PCR Data/Raw data/080714-Dong-IGLL5-10ul-pri-pro-opt.csv", skip = 1, sep = ",", header = T)
```

## 1) Data summary
```{r Data-processing, comment = F, cache=FALSE, message = F, echo= F, warning = F, results='asis', tab.cap ="Sample Summary"}
d <- tbl_df(data)

neg <- filter(d, grepl("[Ne][Ee][Gg]*", d$Sample.Name))

std <- filter(d, Type == "std")
s <-  filter(d, !Type == "std")
cali <- filter(d, Sample.Name == "6x,24-383")
cali.su <- group_by(cali, Pos, Sample.Name) %.% 
                summarize(dCt = Cp[1]-Cp[2], RelQ = 2^-dCt)%.%
                group_by(Sample.Name) %.%
                summarize(dCt.mean = mean(dCt), dCt.sem = sd(dCt)/sqrt(length(dCt)),
                          RelQ.mean = mean(RelQ), RelQ.sem = sd(RelQ)/sqrt(length(RelQ)))

std.su <- group_by(std, Pos, Sample.Name) %.%
        summarize(ddCt = Cp[1]-Cp[2]-cali.su$dCt.mean, RelQ = 2^-ddCt) %.%
        group_by(Sample.Name) %.%
        summarize(ddCt.mean = mean(ddCt), ddCt.sem = sd(ddCt)/sqrt(length(ddCt)),
                  RelQ.mean = mean(RelQ), RelQ.sem = sd(RelQ)/sqrt(length(RelQ)))
        std.su <- std.su[c(1,2,4,5),]


sample <- s
sample.su <- group_by(sample, Pos, Sample.Name) %.% 
        summarize(ddCt = Cp[1]-Cp[2]-cali.su$dCt.mean, RelQ = 2^-ddCt) %.%
        group_by(Sample.Name) %.%
        mutate(var.RelQ = (RelQ - mean(RelQ)) %>% abs) %>%
        filter(var.RelQ != var.RelQ %>% max) %>%
        summarize(ddCt.mean = mean(ddCt), ddCt.sem = sd(ddCt)/sqrt(length(ddCt)),
                  RelQ.mean = mean(RelQ), RelQ.sem = sd(RelQ)/sqrt(length(RelQ)))
sample.su$Sample.Name = toupper(sample.su$Sample.Name)
kable(sample.su, align = "c", digits = 2)
```

## 2) Standard curve

```{r Standard-curve - table, cache=FALSE, message = FALSE, echo=FALSE, results='asis', tab.cap ="Standard Curve"}
if (!exists("std")){
        std.curve <- data.frame(ratio = c("1-1","1-2","1-3"),
                         dCt = c(1.2000464, 0.9563856, 0.6797154),
                         RelQ = c(0.4354689, 0.5153470, 0.6243136),
                         copy.number = c(2,4,6))
        std.lm <- lm(copy.number ~ RelQ , data = std.curve)
        } else {
                std.curve <- data.frame(ratio = std.su$Sample.Name, ddCt = std.su$ddCt.mean, RelQ = std.su$RelQ.mean, RelQ.sem = std.su$RelQ.sem, copy.number = c(5,6,9,9))
                std.lm <- lm(copy.number ~ RelQ , data = std.curve)
        }

kable(std.curve, align = "c", digits = 2)
```


```{r Standard-curve - plot, cache=FALSE, message = FALSE, echo=FALSE, results='asis', fig.align='left'}
ggplot(data = std.curve, aes(y = RelQ, x = as.numeric(copy.number)))+
        geom_point(size = 3) +
        labs(x = "Copy Number", y = "Relative Amount", title = "Standard curve of DEFA1A3")+
        theme_bw()+
        geom_smooth(method = 'lm')+
        ylim(0, 2.6)+
        xlim(0, 9.2)
#         geom_point(aes(x = round(predicted.CN, 2), y = 0))
#         xlim(0,0.7)+
#         ylim(0,7)

estimated.CN <- as.numeric(predict(std.lm, data.frame(RelQ = sample.su$RelQ.mean)))


```

Figure 1: Standard Curve with reference samples

## 3) Copy typing
```{r Copy-number-estimation - table, cache=FALSE, message = FALSE, echo=FALSE, results='asis', tab.cap ="Copy number prediction"}
sample.su$Copy.Nbs.round = round(predict(std.lm, 
                                    data.frame(RelQ = sample.su$RelQ.mean)))

sample.su$Copy.Nbs.esti = predict(std.lm, 
                                     data.frame(RelQ = sample.su$RelQ.mean))
sample.su$Sample.Name = toupper(sample.su$Sample.Name)
kable(sample.su[c(1,6,7)], align = "c", digits = 2)

diff <- abs(sample.su$Copy.Nbs.esti-sample.su$Copy.Nbs.round)

```

```{r Copy-number-estimation - plot, cache=FALSE, message = FALSE, echo=FALSE, results='asis', eval = F}
std.lm.t <- lm(RelQ ~ copy.number, data = std.curve)
ggplot(data = sample.su, aes(x = RelQ.mean, fill = Sample.Name))+
        geom_histogram(binwidth = 0.02)+
        geom_vline(xintercept = predict(std.lm.t, 
                                        data.frame(copy.number = c(1,2,3,4,5,6,7,8,9))))+
        theme_gray()+
        theme(legend.position = "none")

```

#### _Note_:  
-  The following sample(s) might have vague estimation(s) of copy numbers: ***`r filter(sample.su, diff > 0.40)$Sample.Name`***.    
-  The following sample(s) might have high SEM(s) : ***`r filter(sample.su, ddCt.sem > 0.1)$Sample.Name`*** (***`r filter(sample.su, ddCt.sem > 0.1)$ddCt.sem`***).

 
```{r hist, cache=FALSE, message = FALSE, echo=FALSE, results='asis', warning=F, eval= F}
ggplot(data = sample.su, aes(x = factor(Copy.Nbs.round)))+
        geom_histogram(binwidth=0.3)+
        labs(x = "Copy Numbers(round)")+
        theme_bw()

# hist(sample.su$RelQ.mean)
## 4) Supplementary analysis    
```   

Figure 2: Distribution of copy numbers 

## 4) Validation

```{r read-in-RIVUR-data, results = 'asis', echo = F }
defa1a3 <- read.csv("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/Data/RIVUR data/RIVUR_DEFA1A3.csv", header = T)

sample.su[c(1,6,7,5)]$Sample.Name = toupper(sample.su[c(1,6,7)]$Sample.Name)

data.merge = merge(defa1a3, sample.su[c(1,6,7,5)], by.x = "KID", by.y = "Sample.Name", all = T)

data.merge = filter(data.merge, !is.na(Copy.Nbs.esti))%.%
        select(KID, raw.CN, Copy.Nbs.esti, Sex, UTI, Age, Race, RelQ.sem)

data.merge$Copy.Nbs.esti = data.merge$Copy.Nbs.esti
kable(data.merge, align = "c")

```


```{r analysis plot, eval = F, echo = F }
ggplot(data = data.merge, aes(x = Race, y = raw.CN)) +
        geom_bar(stat = "identity", position = "dodge") +
        theme_bw() 
# + 
#         facet_grid(.~ UTI)
        

ggplot(data = data.merge, aes(x =  raw.CN, y = Age, fill = Sex))+
        geom_point()

```


```{r validate - plot, results = 'asis', echo = F , eval = T}
science_theme = theme(panel.grid.major = element_line(size = 0.5, color = "grey"),
                      axis.line = element_line(size = 0.7, color = "black"), 
                      legend.position = "none", 
#                       legend.position = c(0.15, 0.85), 
                      text = element_text(size = 14))

ggplot(data = data.merge, aes(x = Copy.Nbs.esti, y = raw.CN)) +
        geom_point() +
#         geom_smooth(method = "lm") +
#         xlim(c(2.5,12)) +
#         ylim(c(2.5,12)) +        
        geom_text(aes(label = KID, hjust = -0.3), col = "black", size = 3)+
        geom_text(aes(label = RelQ.sem %>% round(2), vjust = 2), col = "blue", size = 3)+

#         geom_text(aes(x = Copy.Nbs.esti, y = raw.CN, label = KID))+
        theme_bw() +
        science_theme

# hist(data.merge$Copy.Nbs.esti)
```

Figure 2: Correlation between two copy number calls


```{r r square, echo = F, eval = F}
corr.lm <- lm(raw.CN ~ Copy.Nbs.esti, data = data.merge)

print(summary(corr.lm))
```

```{r data load}
summary_data <- function(data) {
        d <- tbl_df(data)
        neg <- filter(d, grepl("[Ne][Ee][Gg]*", d$Sample.Name))

        std <- filter(d, Type == "std")
        s <-  filter(d, !Type == "std")
        cali <- filter(d, Sample.Name == "6x,24-383")
        cali.su <- group_by(cali, Pos, Sample.Name) %.% 
                        summarize(dCt = Cp[1]-Cp[2], RelQ = 2^-dCt)%.%
                        group_by(Sample.Name) %.%
                        summarize(dCt.mean = mean(dCt), dCt.sem = sd(dCt)/sqrt(length(dCt)),
                                  RelQ.mean = mean(RelQ), RelQ.sem = sd(RelQ)/sqrt(length(RelQ)))
        
        std.su <- group_by(std, Pos, Sample.Name) %.%
                summarize(ddCt = Cp[1]-Cp[2]-cali.su$dCt.mean, RelQ = 2^-ddCt) %.%
                group_by(Sample.Name) %.%
                summarize(ddCt.mean = mean(ddCt), ddCt.sem = sd(ddCt)/sqrt(length(ddCt)),
                          RelQ.mean = mean(RelQ), RelQ.sem = sd(RelQ)/sqrt(length(RelQ)))
                std.su <- std.su[c(1,2,4,5),]
        
        
        sample <- s
        sample.su <- group_by(sample, Pos, Sample.Name) %.% 
                summarize(ddCt = Cp[1]-Cp[2]-cali.su$dCt.mean, RelQ = 2^-ddCt) %.%
                group_by(Sample.Name) %.%
                summarize(ddCt.mean = mean(ddCt), ddCt.sem = sd(ddCt)/sqrt(length(ddCt)),
                          RelQ.mean = mean(RelQ), RelQ.sem = sd(RelQ)/sqrt(length(RelQ)))
        sample.su$Sample.Name = toupper(sample.su$Sample.Name)
        return(sample.su)
}


data_D <- read.table("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/Data/Raw data/071614-Dong-DEFA1A3-newPriPro.csv", skip = 1, sep = ",", header = T)
data_fit <- read.table("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/Data/Raw data/071614-Dong-DEFA1A3-newPriPro(Fit).csv", skip = 1, sep = ",", header = T)

data_old_fit <- read.table("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/Data/Raw data/070114-Dong-DEFA1A3bis.csv", skip = 1, sep = ",", header = T)

data_old_D <- read.table("/Users/DL/Dropbox-work/My work-not sync/Protocol/Protocol Memphis/Data/Raw data/070114-Dong-DEFA1A3.csv", skip = 1, sep = ",", header = T)


data_D_su <- summary_data(data_D)
data_fit_su <- summary_data(data_fit)
data_old_fit_su <- summary_data(data_old_fit)
data_old_D_su <- summary_data(data_old_D)

```



```{r cor fit vs D, fig.height = 8, fig.width = 10, echo = F, eval = T}
science_theme = theme(panel.grid.major = element_line(size = 0.5, color = "grey"),
                      axis.line = element_line(size = 0.7, color = "black"), 
                      legend.position = "none", 
#                       legend.position = c(0.15, 0.85), 
                      text = element_text(size = 14))


data_mer_fit_D <- merge(data_fit_su, data_D_su, by = "Sample.Name")
data_mer_fit_D %>% 
ggplot( aes(x = RelQ.mean.x, y = RelQ.mean.y )) + 
        geom_point() + 
#         geom_smooth(method = "lm") + 
        geom_text(aes(label = RelQ.sem.y %>% round(2), vjust = 2), col = "blue")+
        geom_text(aes(label = RelQ.sem.x %>% round(2), vjust = -1), col = "red") +
        geom_text(aes(label = Sample.Name, hjust = -0.3), col = "black", size = 3)+
        theme_classic()+
        science_theme

```
Figure 3: Correlation between two calls using different algorithm (FP vs SMD)



```{r cor - fit point, fig.height = 8, fig.width = 10, echo = F}

data_mer_fit <- merge(data_old_fit_su, data_fit_su, by = "Sample.Name")


data_mer_fit %>% 
ggplot( aes(x = RelQ.mean.x, y = RelQ.mean.y )) + 
        geom_point() + 
#         geom_smooth(method = "lm") + 
        geom_text(aes(label = RelQ.sem.x %>% round(2), vjust = 2), col = "blue")+
        geom_text(aes(label = RelQ.sem.y %>% round(2), vjust = -1), col = "red") +
        geom_text(aes(label = Sample.Name, hjust = -0.3), col = "black", size = 3)+
        theme_classic() +
        science_theme
        
```
Figure 4: Correlation between two calls using different sets of primers and probes (Fit points)


```{r cor D, fig.height = 8, fig.width = 10, echo = F, eval = T}
science_theme = theme(panel.grid.major = element_line(size = 0.5, color = "grey"),
                      axis.line = element_line(size = 0.7, color = "black"), 
                      legend.position = "none", 
#                       legend.position = c(0.15, 0.85), 
                      text = element_text(size = 14))


data_mer_D <- merge(data_old_D_su, data_D_su, by = "Sample.Name")
data_mer_D %>% 
ggplot( aes(x = RelQ.mean.x, y = RelQ.mean.y )) + 
        geom_point() + 
#         geom_smooth(method = "lm") + 
        geom_text(aes(label = RelQ.sem.x %>% round(2), vjust = 2), col = "blue")+
        geom_text(aes(label = RelQ.sem.y %>% round(2), vjust = -1), col = "red") +
        geom_text(aes(label = Sample.Name, hjust = -0.3), col = "black", size = 3)+
        theme_classic()+
        science_theme

```
Figure 5: Correlation between two calls using different sets of primers and probes (SMD)



